A multiverse analysis of the associations between internet use and well-being

### 2022-12-16 ms.Rmd
Small ms edits

specs_reyear <- expand_grid(
  distinct(dat_mv_reyear, sex, age),
  y = ys,
  x = xs,
  covariate = cs,
  weights = c("No", "Yes")
) %>% 
  mutate(
    formula = str_glue("{y} ~ {x} + {covariate} + ({x} | country) + ({x} | year) + ({x} | country:year)")
  )
```

@@

fits <- rename(fits, weights = model) %>% 
  filter(n > 0)
fits_gwb <- fits %>% filter(str_detect(y, "gwb_"))
fits <- fits %>% filter(!str_detect(y, "gwb_"))

# Counts for text
n_specs_all <- fits %>% 
  filter(effect == x)
n_specs_main <- n_specs_all %>% 
  filter(!str_detect(y, "gwb_")) %>% 
  nrow() %>% 
  number2()
n_specs_gwb <- n_specs_all %>% 
  filter(str_detect(y, "gwb_")) %>% 
  nrow() %>% 
  number2()
n_specs_all <- n_specs_all %>% 
  nrow() %>% 
  number2()

mv <- fits %>% 
  filter(term == x) %>% 
  arrange(estimate, y) %>% 
  group_by(y) %>% 
  mutate(i = 1:n()) %>% 
  ungroup() %>% 
  mutate(sig = sign(conf.low) == sign(conf.high)) %>% 
  mutate(
    decision = case_when(
      conf.low < 0 & conf.high < 0 ~ "Negative",
      conf.low > 0 & conf.high > 0 ~ "Positive",
      !sig ~ "Not significant"
    ) %>% 
      factor(levels = c("Negative", "Not significant", "Positive"))
  )

@@

---
abstract: |
  With the increasing global penetration of the internet, and technologies and platforms enabled by it, their potential effects on individuals' well-being remains hotly debated. On one hand, these technologies have enabled novel forms of commerce, education, and leisure; on the other, many are worried that their use might negatively affect individuals by, for example, displacing time spent on other healthy activities. Moreover, research findings on the effects of internet technologies on well-being have been mixed and, to date, inconclusive and of limited geographic and demographic scope. In the current work, we examined the extent to which having internet access, mobile internet access, or being an active internet user affected seven well-being outcomes from `r yr` among `r number2(nrow(dat))` individuals living in `r length(unique(dat$country))` countries. We first tested the extent to which well-being varied as a function of internet connectivity. Then, to go beyond describing average associations, we examined the potential causal effects of internet connectivity on well-being with a multiverse analysis over `r n_specs_all` plausible model and subgroup specifications. `r percent(mvs$Positive[5], .01)` of these specifications indicated that internet connectivity was associated with positive well-being, while only `r percent(mvs$Negative[5], .01)` indicated negative associations. These results indicate that internet access and active use are positive contributors to individuals' well-being.
---

@@

$$
\begin{align*} 
y_{ij} &\sim \text{Normal}(\mu_{ij}, \sigma^{2}), \\
\mu_{ij} &= \alpha_{0} + \beta_{0j} +
  (\alpha_{1} + \beta_{1j})(x_{ij} - \bar{x}_{.j}), \\
\begin{bmatrix} 
\beta_0 \\ \beta_1 
\end{bmatrix} 
& \sim\text{Normal}\left(
  \begin{bmatrix}
  0 \\ 0 
  \end{bmatrix}, 
  \begin{bmatrix} 
  \sigma_{\beta_0}^2 & \\ \sigma_{\beta_0\beta_1} & \sigma_{\beta_1}^2 
  \end{bmatrix} 
\right).
\end{align*}
$$

In this manner, $\alpha_1$ is the difference in well-being indicator $y$ between individuals who had access to the internet and those who didn't, for the average country. For our second, primary, research question we then conducted a multiverse analysis over different covariate permutations on this base model and subgroups in the data. We analysed all the possible ways in which the covariates could be included in this model as fixed effects (including no covariates), leading to XXX different covariate specifications. In addition to model specifications and subgroups, GWP recommends using model weights to adjust for demographic representativeness in some analyses, and so we conducted the analyses both with and without model weights. Our multiverse therefore consisted of all the distinct combinations of outcomes, predictors, age, sex, years, covariate combinations, and whether model weights were included or not, leading to `r number2(n_specs_all)` specifications. (This number was smaller than the theoretical number of specifications, because not all combinations were possible (e.g. mobile internet access did not exist before 2017)).

Because an additional concern with this analytic strategy was a diminishing sample size per analysis (reported below), we conducted a second multiverse analysis as a robustness check. That analysis was otherwise similar to our main multiverse analysis, but instead of subgrouping data by year we used year and its interaction with countries as random effect clusters in the multilevel model. In addition to examining the robustness of our results, this additional analysis was motivated by our prior study, where differences in technology-use and well-being associations over time were very small [@vuorreThereNoEvidence2021]. We report this robustness analysis in Appendix B. We used R [@rcoreteamLanguageEnvironmentStatistical2022] for analyses and the lme4 package for estimating the multilevel models [batesFittingLinearMixedEffects2015].

@@

```{r}
path <- "tmp/fits-lmer-total.rds"
if (!file.exists(path)) {

@@

  fits_avg <- expand_grid(
    y = c(
      "life_satisfaction",
      "negative_experiences",
      "positive_experiences",
      "social_life",
      "gwb_purpose", "gwb_social", "gwb_physical"
    ),
    x = c(
      "internet_access",
      "internet_past7days",
      "internet_phone"
    )
  ) %>% 
    mutate(
      model = "No",
      formula = str_glue("{y} ~ {x} + ({x} | country)")
    ) %>% 
    mutate(
      out = future_pmap(
        list(model, formula),
        ~do.call(
          what = ..1, 
          args = list(
            formula = ..2, 
            data = dat2
          )
        ),
        .options = opts
      )
    ) %>% 
    ungroup() %>% 
    unnest(out)

  fits_avg <- fits_avg %>% 
    filter(term == x) %>% 
    select(-c(effect, group, term, model, formula))

  saveRDS(fits_avg, path)
} else {fits_avg <- readRDS(path)}

# Median association (with reversed negative experiences)
tmp <- fits_avg %>% 
  mutate(estimate = if_else(y == "negative_experiences", -1*estimate, estimate)) %>% 
  summarise(across(c(estimate, std.error), median))
```

@@

tmp1 %>% 
  ggplot(aes(x, value)) +
  scale_color_brewer(
    "Difference",
    palette = "Set1"
  ) +
  scale_y_continuous(
    "Well-being mean",
    breaks = extended_breaks(7),
    expand = expansion(.1)
  ) +
  scale_x_discrete(
    "Internet",
    expand = expansion(0.4),
    labels = ~str_replace(., "z", "Y-N")
  ) +
  geom_hline(yintercept = 0, linewidth = .1) +
  geom_line(
    data = . %>% filter(x != "z"),
    aes(group = country),
    linewidth = .1, alpha = .5, col = "gray70",
    position = position_quasirandom(width = .45)
  ) +
  geom_point(
    alpha = .55, size = .8, shape = 1, stroke = .33, 
    col = "gray70", fill = "white",
    position = position_quasirandom(width = .45)
  ) +
  geom_pointrange(
    data = tmp2 %>% filter(x %in% c("No", "Yes")),
    aes(y = y, ymin = ymin, ymax = ymax),
    size = 0.5, fatten = 1.8
  ) +
  geom_pointrange(
    data = tmp2 %>% filter(!(x %in% c("No", "Yes"))),
    aes(y = y, ymin = ymin, ymax = ymax, color = decision),
    size = 0.5, fatten = 1.5
  ) +
  geom_line(
    data = tmp2 %>% filter(x %in% c("No", "Yes")),
    aes(y = y),
    linewidth = .33,
    group = 1,
    show.legend = FALSE
  ) +
  geom_label(
    data = fits_avg %>% 
      filter(!str_detect(y, "gwb_")) %>% 
      mutate(
        across(c(where(is.numeric), -n), ~number(., .001)),
        n = number2(n),
        name = x, x = "No", outcome = y
        ),
    aes(
      label = str_glue("b = {estimate}\n[{conf.low}, {conf.high}]")
    ),
    x = -Inf, y = -Inf, 
    size = 2.7, hjust = 0, vjust = 0, lineheight = 1, fill = NA,
    label.size = 0, label.padding = unit(0.5, "line")
  ) +
  facet_grid(
    name ~ outcome, 
    labeller = as_labeller(~sanitize_labels(.))
  ) +
  theme(
    legend.position = "bottom"
  )
```

@@

```{r}
#| label: tbl-multiverse
#| include: true
out_sum_2 <- out_sum_2 %>% 
  mutate(
    N = number2(N, 1),
    across(c(Negative, `Not significant`, Positive), ~percent(., .01)),
    across(c(`0.25`, `0.5`, `0.75`), ~number(., .01))
  ) %>% 
  mutate(
    Median = `0.5`,
    IQR = str_glue("[{`0.25`}, {`0.75`}]"),
    .keep = "unused",
    .after = 2
  )
out_sum_2 %>%   
  apa_table(
    caption = "Summary of multiverse analysis of associations between internet access (or use) and well-being.", 
    note = 'N is the median sample size across specifications. "Total" indicates quantities across well-being outcomes (we reversed associations with negative experiences for this aggregate number).', 
    col_spanners = list(
      "Association magnitude" = c(3, 4),
      "Proportions of significant associations" = c(5, 7)
    ), 
    placement = "ht"
  )
```

@@

```{r}
#| include: true
#| label: fig-multiverse
#| out.width: "\\textwidth"
#| fig.env: "figure*"
#| fig.height: 7.6
#| fig.width: 9
#| fig.cap: Multiverse analysis results of associations between three internet use predictors and four well-being outcomes. A. Estimated associations, in order of increasing magnitude, shown separately for each of the four main well-being outcomes. The small shaded areas to the right of each panel show the kernel density estimates of the associations' point estimates, and the median association with a colored point. B. A dashboard of model specifications. Each point in the small panels indicates the value of the grouping variable or covariate specification for the model indicated on the x-axis.

p1 <- out %>% 
  ggplot(aes(i, estimate, col = decision)) +
  scale_color_manual(values = c("firebrick2", "grey70", "dodgerblue2")) +
  scale_y_continuous(position = "right",
    "Estimated association (95%CI)",
    breaks = extended_breaks(7)
  ) +
  scale_x_continuous(
    "Analysis specification (in order of association magnitude)",
    breaks = extended_breaks(5),
    expand = expansion(.015)
  ) +
  geom_hline(yintercept = 0, linewidth = .1) +
  geom_point(size = .25) +
  geom_linerange(
    aes(ymin = conf.low, ymax = conf.high),
    linewidth = .2, alpha = .2
  ) +
  geom_ysidedensity(
    aes(x = after_stat(ndensity)), 
    col = "grey20", fill = "grey60", alpha = .4, n = 3001
  ) +
  geom_ysidepoint(
    data = out_sum %>% 
      # Just for coloring the dot
      mutate(
        decision = cut(
          `0.5`, 
          breaks = c(-1, -.0001, .0001, 1), 
          labels = levels(out$decision)
        )
      ),
    aes(y = `0.5`, x = 0),
    size = 2, position = position_nudge(x = .025)
  ) +
  scale_ysidex_continuous(expand = expansion(c(0, .2))) +
  facet_wrap(
    "y", 
    scales = "free_x", 
    nrow = 1, 
    drop = TRUE,
    labeller = as_labeller(sanitize_labels)
    ) +
  theme(
    axis.title.x = element_blank(),
    legend.position = "none",
    ggside.panel.scale = 0.1,
    ggside.panel.spacing.x = unit(0, "pt"),
    ggside.axis.text = element_blank(),
    ggside.axis.ticks = element_blank()
  )

p2 <- out %>% 
  mutate(
    weights = factor(
      weights, 
      levels = c("No", "Yes"), 
      labels = c("No weights", "Weights"))
  ) %>% 
  pivot_longer(
    c(year, age, sex, x, covariate, weights), 
    values_transform = as.character
  ) %>%
  mutate(
    name = factor(
      name, 
      levels = c("x", "age", "sex", "covariate", "year", "weights"),
      labels = c("X", "Age", " ", "Covariates", "Year", "  ")
    ),
    value = fct_relevel(value, unique(specs$covariate)),
    value = fct_recode(value, `No covariates` = "1")
  ) %>% 
  ggplot(aes(i, value, col = decision)) +
  scale_color_manual(values = c("firebrick2", "grey70", "dodgerblue2")) +
  scale_y_discrete(
    position = "right",
    labels = ~sanitize_labels(., FALSE)
  ) +
  scale_x_continuous(
    "Analysis specification (ordered by increasing magnitude of association)",
    breaks = extended_breaks(5),
    expand = expansion(.01)
  ) +
  geom_point(shape = 20, size = .2) +
  facet_grid(
    cols = vars(y),
    rows = vars(name), 
    scales = "free_y", 
    space = "free_y", 
    switch = "y", 
    drop = TRUE,
    labeller = as_labeller(sanitize_labels)
  ) +
  theme(
    axis.text.y = element_text(size = rel(0.6)),
    axis.title.y = element_blank(),
    # axis.text.x = element_blank(),
    legend.position = "none"
  )

((p1 / p2) +
  plot_layout(heights = c(3.6, 6.4))) +
  plot_annotation(tag_levels = "A")
```

```{r}
#| include: true
#| label: fig-multiverse-zoom
#| out.width: "\\textwidth"
#| fig.env: "figure*"
#| fig.cap: Median associations between the internet predictors and well-being outcomes by sex and age, ordered by covariate specification. The specifications are ordered as in Figure 2; where greater numbers indicate more covariates in the model.
p1 <- fits %>% 
  filter(term == x) %>% 
  reframe(
    q = c(.1, .5, .9),
    value = quantile(estimate, probs = c(.1, .5, .9)),
    .by = c(covariate, age, sex, x, y)
  ) %>% 
  pivot_wider(names_from = q) %>% 
  mutate(
    covariate = fct_relevel(covariate, unique(specs$covariate)),
    i = as.numeric(covariate)
  ) %>%
  ggplot(aes(i, `0.5`)) +
  geom_hline(yintercept = 0, size = .1) +
  scale_color_viridis_d(
    "Age"
  ) +
  scale_y_continuous(
    "Median association"
  ) +
  scale_x_continuous(
    "Covariate specification"
  ) +
  geom_line(aes(group = age, col = age)) +
  facet_nested(
    x + sex ~ y,
    labeller = as_labeller(sanitize_labels)
  )

@@

```{r}
fits %>% 
  filter(term == x) %>% 
  reframe(
    q = c(.1, .5, .9),
    value = quantile(estimate, probs = c(.1, .5, .9)),
    .by = c(covariate, age, x, y)
  ) %>% 
  pivot_wider(names_from = q) %>% 
  mutate(
    covariate = fct_relevel(covariate, unique(specs$covariate)),
    covariate = fct_recode(covariate, `No covariates` = "1")
  ) %>%
  ggplot(aes(`0.5`, covariate, col = age)) +
  geom_vline(xintercept = 0, size = .1) +
  scale_color_brewer(palette = "Set1") +
  scale_x_continuous(
    "Estimated association"
  ) +
  ggstance::geom_pointrangeh(
    aes(xmin = `0.1`, xmax = `0.9`),
    size = .1, fatten = 0.25,
    position = position_dodge(width = 1)
  ) +
  facet_nested(
    x ~ y,
    labeller = as_labeller(sanitize_labels)
  )
```

@@

```{r}
#| eval: false
library(ggstance)
library(ggh4x)
fits %>% 
  drop_na(age, sex) %>% 
  filter(
    covariate %in% c("1", "healthproblems + income"),
    !str_detect(y, "gwb"),
    year %% 2 == 1,
    year >= 2015
  ) %>% 
  ungroup() %>% 
  mutate(
    sig = sign(conf.low) == sign(conf.high),
    covariate = factor(
      covariate, labels = c("No covariates", "Income and health problems")
    ),
    color = str_glue("{sex}\n{covariate}")
  ) %>% 
  arrange(sex, covariate) %>% 
  mutate(color = fct_inorder(color)) %>% 
  ggplot(aes(year, estimate, col = color)) +
  scale_color_manual(
    "Model covariates",
    values = c("firebrick1", "firebrick4", "dodgerblue1", "dodgerblue4")
  ) +
  scale_shape_manual(values = c(21, 19)) +
  scale_y_continuous(
    "Estimated association (95%CI)",
    labels = ~percent(., 1)
  ) +
  scale_x_continuous(
    "Year",
    breaks = c(2015, 2017, 2019, 2021),
    labels = ~str_glue("'{str_sub(., 3, 4)}")
  ) +
  geom_hline(yintercept = 0, linewidth = .1) +
  geom_pointrange(
    aes(ymin = conf.low, ymax = conf.high, shape = sig),
    position = position_dodge2(1),
    fatten = 2.5, fill = "white", stroke = .8
  ) +
  guides(shape = "none") +
  facet_nested(
    age ~ y + x, scales = "free_x",
    labeller = as_labeller(sanitize_labels)
  ) +
  theme(
    legend.position = "bottom", 
    legend.title = element_blank()
  )
```

@@

The main thrust of our analysis was to examine to what extent this positive association between internet and well-being was sensitive to different demographic groups, time periods, and modelling decisions. Furthermore, we attempted to estimate the unique contributions of internet on well-being by examining this association across `r length(unique(specs$covariate))` different permutations of sets of plausible covariates that might otherwise create or mask associations. Across `r number2(nrow(filter(fits, term == x)))` of such model specifications, `r out_sum_2$Positive[5]` of the associations were significantly positive, and only `r out_sum_2$Negative[5]` were negative. We thus conclude that the proliferation of (mobile) internet access and increasing engagement with the internet has been a net benefit to the well-being of individuals around the world.

>>>>

specs_reyear <- expand_grid(
  distinct(dat_mv_reyear, sex, age),
  y = ys,
  x = xs,
  covariate = cs,
  weights = c("No", "Yes")
) %>% 
  mutate(
    formula = str_glue(
      "{y} ~ {x} + {covariate} + ({x} | country) + ({x} | year) + ({x} | country:year)"
    )
  )
```

@@

specs_gwb <- specs %>% filter(str_detect(y, "gwb_"))
specs <- specs %>% filter(!str_detect(y, "gwb_"))

n_specs_main <- specs %>% 
  filter(term == x) %>% 
  nrow()
n_specs_gwb <- specs_gwb %>% 
  filter(term == x) %>% 
  nrow()
n_specs_all <- n_specs_main + n_specs_gwb

mv <- specs %>% 
  filter(term == x) %>% 
  arrange(estimate, y) %>% 
  group_by(y) %>% 
  mutate(i = 1:n()) %>% 
  ungroup() %>% 
  mutate(sig = sign(conf.low) == sign(conf.high)) %>% 
  mutate(
    decision = case_when(
      conf.low < 0 & conf.high < 0 ~ "Negative",
      conf.low > 0 & conf.high > 0 ~ "Positive",
      !sig ~ "Not significant"
    ) %>% 
      factor(levels = c("Negative", "Not significant", "Positive"))
  )

@@

---
abstract: |
  With the increasing global penetration of the internet, and technologies and platforms enabled by it, their potential effects on individuals' well-being remains hotly debated. On one hand, these technologies have enabled novel forms of commerce, education, and leisure; on the other, many are worried that their use might negatively affect individuals by, for example, displacing time spent on other healthy activities. Moreover, research findings on the effects of internet technologies on well-being have been mixed and, to date, inconclusive and of limited geographic and demographic scope. In the current work, we examined the extent to which having internet access, mobile internet access, or being an active internet user affected seven well-being outcomes from `r yr` among `r number2(nrow(dat))` individuals living in `r length(unique(dat$country))` countries. We first tested the extent to which well-being varied as a function of internet connectivity. Then, to go beyond describing average associations, we examined the potential causal effects of internet connectivity on well-being with a multiverse analysis over XXXX plausible model and subgroup specifications. `r percent(mvs$Positive[5], .01)` of these specifications indicated that internet connectivity was associated with positive well-being, while only `r percent(mvs$Negative[5], .01)` indicated negative associations. These results indicate that internet access and active use are positive contributors to individuals' well-being.
---

@@

\begin{align*} 
y_{ij} &\sim \text{Normal}(\mu_{ij}, \sigma^{2}), \\
\mu_{ij} &= \alpha_{0} + \beta_{0j} +
  (\alpha_{1} + \beta_{1j})(x_{ij} - \bar{x}_{.j}), \\
\begin{bmatrix} 
\beta_0 \\ \beta_1 
\end{bmatrix} 
& \sim\text{Normal}\left(
  \begin{bmatrix}
  0 \\ 0 
  \end{bmatrix}, 
  \begin{bmatrix} 
  \sigma_{\beta_0}^2 & \\ \sigma_{\beta_0\beta_1} & \sigma_{\beta_1}^2 
  \end{bmatrix} 
\right).
\end{align*}

In this manner, $\alpha_1$ is the difference in well-being indicator $y$ between individuals who had access to the internet and those who didn't, for the average country. For our second, primary, research question we then conducted a multiverse analysis over different covariate permutations on this base model and subgroups in the data. We analysed all the possible ways in which the covariates could be included in this model as fixed effects (including no covariates), leading to XXX different covariate specifications. In addition to model specifications and subgroups, GWP recommends using model weights to adjust for demographic representativeness in some analyses, and so we conducted the analyses both with and without model weights. Our multiverse therefore consisted of all the distinct combinations of outcomes, predictors, age, sex, years, covariate combinations, and whether model weights were included or not, leading to `r n_specs_all` specifications. (This number was smaller than the theoretical number of specifications, because not all combinations were possible (e.g. mobile internet access did not exist before 2017)).

Because an additional concern with this analytic strategy was a diminishing sample size per analysis (reported below), we conducted a second multiverse analysis as a robustness check. That analysis was otherwise similar to our main multiverse analysis, but instead of subgrouping data by year we used year and its interaction with countries as random effect clusters in the multilevel model. In addition to examining the robustness of our results, this additional analysis was motivated by our prior study, where differences in technology-use and well-being associations over time were very small [@vuorreThereNoEvidence2021]. We report this robustness analysis in Appendix B. We used R [@rcoreteamLanguageEnvironmentStatistical2022] for analyses and the lme4 package for estimating the multilevel models [@batesFittingLinearMixedEffects2015].

@@

```{r}
path <- "tmp/specs-lmer-total.rds"
if (!file.exists(path)) {

@@

  specs_avg <- expand_grid(
    y = c(
      "life_satisfaction",
      "negative_experiences",
      "positive_experiences",
      "social_life",
      "gwb_purpose", "gwb_social", "gwb_physical"
    ),
    x = c(
      "internet_access",
      "internet_past7days",
      "internet_phone"
    )
  ) %>% 
    mutate(
      model = "No",
      formula = str_glue("{y} ~ {x} + ({x} | country)")
    ) %>% 
    mutate(
      out = future_pmap(
        list(model, formula),
        ~do.call(
          what = ..1, 
          args = list(
            formula = ..2, 
            data = dat2
          )
        ),
        .options = opts
      )
    ) %>% 
    ungroup() %>% 
    unnest(out)

  specs_avg <- specs_avg %>% 
    filter(term == x) %>% 
    select(-c(effect, group, term, model, formula))

  saveRDS(specs_avg, path)
} else {specs_avg <- readRDS(path)}

# Median association (with reversed negative experiences)
tmp <- specs_avg %>% 
  mutate(estimate = if_else(y == "negative_experiences", -1*estimate, estimate)) %>% 
  summarise(across(c(estimate, std.error), median))
```

@@

tmp1 %>% 
  ggplot(aes(x, value)) +
  scale_color_brewer(
    "Difference",
    palette = "Set1"
  ) +
  scale_y_continuous(
    "Well-being mean",
    breaks = extended_breaks(7),
    expand = expansion(.1)
  ) +
  scale_x_discrete(
    "Internet",
    expand = expansion(0.4),
    labels = ~str_replace(., "z", "Y-N")
  ) +
  geom_hline(yintercept = 0, linewidth = .1) +
  geom_line(
    data = . %>% filter(x != "z"),
    aes(group = country),
    linewidth = .1, alpha = .5, col = "gray70",
    position = position_quasirandom(width = .45)
  ) +
  geom_point(
    alpha = .55, size = .8, shape = 1, stroke = .33, 
    col = "gray70", fill = "white",
    position = position_quasirandom(width = .45)
  ) +
  geom_pointrange(
    data = tmp2 %>% filter(x %in% c("No", "Yes")),
    aes(y = y, ymin = ymin, ymax = ymax),
    size = 0.5, fatten = 1.8
  ) +
  geom_pointrange(
    data = tmp2 %>% filter(!(x %in% c("No", "Yes"))),
    aes(y = y, ymin = ymin, ymax = ymax, color = decision),
    size = 0.5, fatten = 1.5
  ) +
  geom_line(
    data = tmp2 %>% filter(x %in% c("No", "Yes")),
    aes(y = y),
    linewidth = .33,
    group = 1,
    show.legend = FALSE
  ) +
  geom_label(
    data = specs_avg %>% 
      filter(!str_detect(y, "gwb_")) %>% 
      mutate(
        across(c(where(is.numeric), -n), ~number(., .001)),
        n = number2(n),
        name = x, x = "No", outcome = y
        ),
    aes(
      label = str_glue("b = {estimate}\n[{conf.low}, {conf.high}]")
    ),
    x = -Inf, y = -Inf, 
    size = 2.7, hjust = 0, vjust = 0, lineheight = 1, fill = NA,
    label.size = 0, label.padding = unit(0.5, "line")
  ) +
  facet_grid(
    name ~ outcome, 
    labeller = as_labeller(~sanitize_labels(.))
  ) +
  theme(
    legend.position = "bottom"
  )
```

@@

```{r}
#| label: tbl-multiverse
#| include: true
mvs2 <- mvs %>% 
  mutate(
    N = number2(N, 1),
    across(c(Negative, `Not significant`, Positive), ~percent(., .01)),
    across(c(`0.25`, `0.5`, `0.75`), ~number(., .01))
  ) %>% 
  mutate(
    Median = `0.5`,
    IQR = str_glue("[{`0.25`}, {`0.75`}]"),
    .keep = "unused",
    .after = 2
  )
mvs2 %>%   
  apa_table(
    caption = "Summary of multiverse analysis of associations between internet access (or use) and well-being.", 
    note = 'N is the median sample size across specifications. "Total" indicates quantities across well-being outcomes (we reversed associations with negative experiences for this aggregate number).', 
    col_spanners = list(
      "Association magnitude" = c(3, 4),
      "Proportions of significant associations" = c(5, 7)
    ), 
    placement = "ht"
  )
```

@@

```{r}
#| include: true
#| label: fig-multiverse
#| out.width: "\\textwidth"
#| fig.env: "figure*"
#| fig.height: 7.8
#| fig.width: 9
#| fig.cap: Multiverse analysis results of associations between three internet use predictors and four well-being outcomes. A. Estimated associations, in order of increasing magnitude, shown separately for each of the four main well-being outcomes. The small shaded areas to the right of each panel show the kernel density estimates of the associations' point estimates, and the median association with a colored point. B. A dashboard of model specifications. Each point in the small panels indicates the value of the grouping variable or covariate specification for the model indicated on the x-axis.
p1 <- mv %>% 
  ggplot(aes(i, estimate, col = decision)) +
  scale_color_manual(values = c("firebrick2", "grey70", "dodgerblue2")) +
  scale_y_continuous(position = "right",
    "Estimated association (95%CI)",
    breaks = extended_breaks(7)
  ) +
  scale_x_continuous(
    "Analysis specification (in order of association magnitude)",
    breaks = extended_breaks(5),
    expand = expansion(.015)
  ) +
  geom_hline(yintercept = 0, linewidth = .1) +
  geom_point(size = .25) +
  geom_linerange(
    aes(ymin = conf.low, ymax = conf.high),
    linewidth = .2, alpha = .2
  ) +
  geom_ysidedensity(
    aes(x = after_stat(ndensity)), 
    col = "grey20", fill = "grey60", alpha = .4, n = 3001
  ) +
  geom_ysidepoint(
    data = mv %>% 
      group_by(y) %>% 
      summarise(median = median(estimate)) %>% 
      # Just for coloring the dot
      mutate(
        decision = cut(
          median,
          breaks = c(-1, -.0001, .0001, 1),
          labels = c("Negative", "Not significant", "Positive")
        )
      ),
    aes(y = median, x = 0),
    size = 2, position = position_nudge(x = .025)
  ) +
  scale_ysidex_continuous(expand = expansion(c(0, .2))) +
  facet_wrap(
    "y", 
    scales = "free_x", 
    nrow = 1, 
    drop = TRUE,
    labeller = as_labeller(sanitize_labels)
    ) +
  theme(
    axis.title.x = element_blank(),
    legend.position = "none",
    ggside.panel.scale = 0.1,
    ggside.panel.spacing.x = unit(0, "pt"),
    ggside.axis.text = element_blank(),
    ggside.axis.ticks = element_blank()
  )

p2 <- mv %>% 
  mutate(
    weights = factor(
      weights, 
      levels = c("No", "Yes"), 
      labels = c("No weights", "Weights"))
  ) %>% 
  pivot_longer(
    c(year, age, sex, x, covariate, weights), 
    values_transform = as.character
  ) %>%
  mutate(
    name = factor(
      name, 
      levels = c("x", "age", "sex", "covariate", "year", "weights"),
      labels = c("X", "Age", " ", "Covariates", "Year", "  ")
    ),
    value = fct_relevel(value, cs),
    value = fct_recode(value, `No covariates` = "1")
  ) %>%
  ggplot(aes(i, value, col = decision)) +
  scale_color_manual(values = c("firebrick2", "grey70", "dodgerblue2")) +
  scale_y_discrete(
    position = "right",
    labels = ~sanitize_labels(., FALSE)
  ) +
  scale_x_continuous(
    "Analysis specification (ordered by increasing magnitude of association)",
    breaks = extended_breaks(5),
    expand = expansion(.01)
  ) +
  geom_point(
    shape = 20, 
    size = .1, 
    position = position_quasirandom(groupOnX = FALSE, width = .2)
  ) +
  facet_grid(
    cols = vars(y),
    rows = vars(name), 
    scales = "free_y", 
    space = "free_y", 
    switch = "y", 
    drop = TRUE,
    labeller = as_labeller(sanitize_labels)
  ) +
  theme(
    axis.text.y = element_text(size = rel(0.6)),
    axis.title.y = element_blank(),
    # axis.text.x = element_blank(),
    legend.position = "none"
  )

((p1 / p2) +
  plot_layout(heights = c(3.2, 6.8))) +
  plot_annotation(tag_levels = "A")
```

```{r}
#| include: true
#| label: fig-multiverse-zoom
#| out.width: "\\textwidth"
#| fig.env: "figure*"
#| fig.cap: Median associations between the internet predictors and well-being outcomes by sex and age, ordered by covariate specification. The specifications are ordered as in Figure 2; where greater numbers indicate more covariates in the model.
p1 <- specs %>% 
  filter(term == x) %>% 
  reframe(
    q = c(.1, .5, .9),
    value = quantile(estimate, probs = c(.1, .5, .9)),
    .by = c(covariate, age, sex, x, y)
  ) %>% 
  pivot_wider(names_from = q) %>% 
  mutate(
    covariate = fct_relevel(covariate, unique(specs$covariate)),
    i = as.numeric(covariate)
  ) %>%
  ggplot(aes(i, `0.5`)) +
  geom_hline(yintercept = 0, size = .1) +
  scale_color_viridis_d(
    "Age"
  ) +
  scale_y_continuous(
    "Median association"
  ) +
  scale_x_continuous(
    "Covariate specification"
  ) +
  geom_line(aes(group = age, col = age)) +
  facet_nested(
    x + sex ~ y,
    labeller = as_labeller(sanitize_labels)
  )

@@

```{r}
specs %>% 
  filter(term == x) %>% 
  reframe(
    q = c(.1, .5, .9),
    value = quantile(estimate, probs = c(.1, .5, .9)),
    .by = c(covariate, age, x, y)
  ) %>% 
  pivot_wider(names_from = q) %>% 
  mutate(
    covariate = fct_relevel(covariate, unique(specs$covariate)),
    covariate = fct_recode(covariate, `No covariates` = "1")
  ) %>%
  ggplot(aes(`0.5`, covariate, col = age)) +
  geom_vline(xintercept = 0, size = .1) +
  scale_color_brewer(palette = "Set1") +
  scale_x_continuous(
    "Estimated association"
  ) +
  ggstance::geom_pointrangeh(
    aes(xmin = `0.1`, xmax = `0.9`),
    size = .1, fatten = 0.25,
    position = position_dodge(width = 1)
  ) +
  facet_nested(
    x ~ y,
    labeller = as_labeller(sanitize_labels)
  )
```

@@

```{r}
#| eval: false
library(ggstance)
library(ggh4x)
specs %>% 
  drop_na(age, sex) %>% 
  filter(
    covariate %in% c("1", "healthproblems + income"),
    !str_detect(y, "gwb"),
    year %% 2 == 1,
    year >= 2015
  ) %>% 
  ungroup() %>% 
  mutate(
    sig = sign(conf.low) == sign(conf.high),
    covariate = factor(
      covariate, labels = c("No covariates", "Income and health problems")
    ),
    color = str_glue("{sex}\n{covariate}")
  ) %>% 
  arrange(sex, covariate) %>% 
  mutate(color = fct_inorder(color)) %>% 
  ggplot(aes(year, estimate, col = color)) +
  scale_color_manual(
    "Model covariates",
    values = c("firebrick1", "firebrick4", "dodgerblue1", "dodgerblue4")
  ) +
  scale_shape_manual(values = c(21, 19)) +
  scale_y_continuous(
    "Estimated association (95%CI)",
    labels = ~percent(., 1)
  ) +
  scale_x_continuous(
    "Year",
    breaks = c(2015, 2017, 2019, 2021),
    labels = ~str_glue("'{str_sub(., 3, 4)}")
  ) +
  geom_hline(yintercept = 0, linewidth = .1) +
  geom_pointrange(
    aes(ymin = conf.low, ymax = conf.high, shape = sig),
    position = position_dodge2(1),
    fatten = 2.5, fill = "white", stroke = .8
  ) +
  guides(shape = "none") +
  facet_nested(
    age ~ y + x, scales = "free_x",
    labeller = as_labeller(sanitize_labels)
  ) +
  theme(
    legend.position = "bottom", 
    legend.title = element_blank()
  )
```

@@

The main thrust of our analysis was to examine to what extent this positive association between internet and well-being was sensitive to different demographic groups, time periods, and modelling decisions. Furthermore, we attempted to estimate the unique contributions of internet on well-being by examining this association across `r length(unique(specs$covariate))` different permutations of sets of plausible covariates that might otherwise create or mask associations. Across `r number2(nrow(filter(specs, term == x)))` of such model specifications, `r mvs$Positive[5]` of the associations were significantly positive, and only `r mvs$Negative[5]` were negative. We thus conclude that the proliferation of (mobile) internet access and increasing engagement with the internet has been a net benefit to the well-being of individuals around the world.
